White Dwarf Mergers on Adaptive Meshes\\ I. Methodology and Code Verification

### 2015-12-17 papers/wdmerger_I/submit/paper.tex
Add a copy of the files that were submitted to ApJ for paper 1

\documentclass[iop,numberedappendix]{../emulateapj}

@@

As a demonstration of the method's accuracy, we consider the case of two 
white dwarfs of mass ratio 2/3, using the initialization procedure described below 
in \autoref{sec:implementation}. We terminated the simulation just after
initialization, so that we perform only an initial Poisson solve for this 
density distribution. We did this for values of $l_{\text{max}}$ ranging
from 0 to 20, and we also did this using the numerically exact solution 
provided by \autoref{eq:direct_sum}.  Defining the $L^2$
norm of a field $f$ as
\begin{equation}
  \| f \|_2 = \left(\sum_{i,j,k} \Delta x\, \Delta y\, \Delta z\, f_{ijk}^2\right)^{1/2},
\end{equation}
we computed the $L^2$ error of $\Phi$ on the entire domain for multipole 
boundary conditions, which we call $\Phi_l$, relative to $\Phi$ 
obtained using the exact boundary conditions:
\begin{equation}
  \text{Error}_l = \frac{\|\Phi_l - \Phi_{\text{exact}}\|_2}{\|\Phi_{\text{exact}}\|_2}.
\end{equation}
The result is shown in \autoref{fig:bc_comparison}. At $l_{\text{max}} = 6$,
the error is already well below $10^{-4}$ and we adopt this as our default 
choice for all simulations with Poisson gravity. In \autoref{sec:kepler} we 
show that there are no gains to be had by increasing the accuracy further. At 
very high orders ($l \gtrsim 18$) the approximation breaks down, as seen in \autoref{fig:bc_comparison}. 
This is a result of the ambient material on the grid. At each boundary point we 
assume that all of the mass on the grid is contained within a sphere whose radius is 
the distance from that boundary point to the center of the domain. This does not hold 
for boundary points in the centers of domain faces, because of the material in the 
domain corners. This can be fixed by using multiple mass shells at diferent radii, but the error 
is negligible in practice for the values of $l_{\text{max}}$ that we use.
\begin{figure}[h]
  \centering
  \includegraphics[scale=0.45]{plots/bc_comparison}
  \caption{Error of $\Phi$ on the computational domain for a binary white dwarf simulation 
    whose boundary conditions were computed using various values of the maximum multipole order,
    relative to the exact solution determined by a brute force sum on the boundaries.
    Circles represent the error at integer values, and they have been connected by a smooth 
    line to guide the eye.\label{fig:bc_comparison}}
\end{figure}

@@

We find that at low resolution convergence is actually substantially better 
than second-order. The explanation for this is that we are attempting to 
model a spherical object on a rectangular grid. This results in two sources of error.
First, at very low resolution, the object does not look very spherical due to the rectangular 
grid representation, so the potential it produces is not quite that of a sphere. 
As the resolution is increased, the distribution of the mass on the grid will change.
\begin{figure}[h]
  \centering
  \includegraphics[scale=0.45]{plots/phi_comparison}
  \caption{Comparison of the \castro\ gravitational potential to the analytical solution for: 
    a sphere of uniform density; the same sphere, but with the potential normalized using the 
    actual amount of mass on the grid instead of the mass of a perfect sphere; and, a 
    cube of uniform density. Plotted also is a notional curve whose slope represents
    perfect second order convergence.\label{fig:gravity_convergence}}
\end{figure}
Second, the total amount of mass on the grid will change as the sphere fills out. 
So we are combining the true accuracy bonus from increased resolution 
with the artificial accuracy bonus from getting closer to solving the problem 
we are supposed to be solving. At high resolution this effect levels off, though, 
as the representation of the sphere is not significantly different in 
our two highest resolutions shown. For example, at $128$ zones per dimension 
the amount of mass on the grid happens to be slightly closer to the true spherical 
mass than at $256$ zones per dimension.
We can eliminate the second source of error by changing the density on  
the grid so that the total mass $M$ is actually what we intend it to be.
The resolution study for this case (the ``normalized sphere'') is also
plotted in \autoref{fig:gravity_convergence}. At low resolution we still obtain
convergence slightly better than second-order, indicating that we 
have not eliminated the geometrical problem of the mass distribution changing.

@@

Outside of the stars we fill the rest of the domain with a very low density 
ambient gas because our hydrodynamics model requires the density to be 
non-zero everywhere. This ambient material can create difficulties for the simulation.
In addition to the negative densities or energies at the stellar surfaces mentioned earlier, 
in the rotating reference frame we observe that standing instabilities can create very 
large velocities in the ambient fluid that drag down the global timestep by 
up to an order of magnitude.  To deal with this we employ a ``sponge'' similar 
to that described by \citet{maestro3} for the outer regions of the computational domain. 
After the hydrodynamics update, we apply a damping force to the momentum
equation as follows:
\begin{equation}
  (\rho \mathbf{u})^{n+1} \to \frac{(\rho \mathbf{u})^{n+1}}{1 + (\Delta t / \Delta t_S) f_S},
\end{equation} 
where $\Delta t_S$ is a timescale for the sponge to operate on, and
$f_S$ is the damping factor.  We choose it so that that the sponge is
non-operational inside a radius $r_S$ from the origin, and fully
applied at a radius $r_S^\prime \equiv r_S + \Delta r_S$. We then
smooth the sponge out between $r_S$ and $r_S^\prime$:
\begin{equation}
  f_{S} = \begin{dcases} 0 & r < r_S \\ \frac{1}{2}\left(1 - \text{cos}\left[\pi\left(\dfrac{r - r_S}{\Delta r_S}\right)\right]\right) & r_S \leq r < r_S^\prime \\ 1 & r \geq r_S^\prime. \end{dcases}\label{eq:sponge_frac}
\end{equation}
For the simulations in this paper we set $r_S$ to be 75\% of the 
distance from the origin to the domain boundaries, and $\Delta r_S$ so
that the sponge smoothing region extends another 10\% of that distance.
The resulting profile is displayed in \autoref{fig:sponge}. We set $\Delta
t_S = 0.01$ s, which is of the same order as the CFL timestep
for typical problem setups. While the sponge is applied we should avoid imputing any physical 
meaning to what is happening in the low-density gas far from the stars.
\begin{figure}
  \centering
  \includegraphics[scale=0.4]{plots/sponge}
  \caption{Radial profile of the hydrodynamical sponge we apply (\autoref{eq:sponge_frac}). 
           We subtract $f_S$ from unity; the value of $1 - f_S$ indicates what happens 
           to the sponged function after the sponge is applied. The sponge has no effect 
           in the inner part of the domain, and is fully applied at the outer edge.\label{fig:sponge}}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[scale=0.45]{plots/single_star_static_1e3_radius}
  \caption{Time evolution of the effective radius of a $0.9 \msolar$ 
    white dwarf, seeded onto the grid using a one-dimensional hydrostatic
    model and evolved without further relaxation. The lines represent 
    different number of zones per spatial dimension; when this number is 
    greater than 256, it represents an effective resolution obtained 
    using AMR levels that cover the star. The radius is determined 
    using the volume of the grid that has a density greater than $10^3\ \text{g cm}^{-3}.$
    \label{fig:single_star_static_radius}}
\end{figure}

@@

We loaded a single star of mass $0.9\ \msolar$ onto the grid at the
origin, and evolved it for 200 seconds. Our diagnostic of choice is
the effective radius of the star, determined by the volume of the grid
that has a density greater than $10^3\ \text{g cm}^{-3}$ (see
\autoref{sec:implementation} for details on this measure). This choice
of density is intended to mark a reasonable outer edge to the star
that is not immediately susceptible to the numerical errors prevalent
near the physical edge of the star.
\autoref{fig:single_star_static_radius} shows our results at various
resolutions.  As expected, the star quickly approaches an equilibrium
size that is different (and in this case larger) than the
one-dimensional model, though the magnitude of this change becomes
smaller with resolution. The star is only approximately in equilibrium 
by this measure when the coarse grid of $256^3$ zones has a level of 
refinement that jumps by a factor of four. Even then there is a slight uptick
in the size toward the end, implying that the numerical stability is
not guaranteed for arbitrarily long timescales. For another view, we 
consider the kinetic energy on the grid, in \autoref{fig:single_star_static_ke}. 
This is a more holistic measure that weights the contribution by the density. 
At the end of the simulation the kinetic energy is not lower at the highest 
resolution than at the lower resolutions. This result suggests
that when constructing the equilibrium initial models that will form the
basis of later calculations, we should carefully monitor the evolution
of the stars when applying any artificial damping to cause the
merger, to ensure that the merger is due to this applied force and not
the intrinsic numerical instability of the stars.
\begin{figure}
  \centering
  \includegraphics[scale=0.45]{plots/single_star_static_ke}
  \caption{Time evolution of the kinetic energy of a $0.9\, \msolar$ 
    white dwarf. The lines have the same meaning as in \autoref{fig:single_star_static_radius}.
    \label{fig:single_star_static_ke}}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[scale=0.45]{plots/freefall}
  \caption{Time evolution of two initially stationary white dwarfs,
    mutually attracted to each other by the gravitational force. The
    horizontal axis gives the separation of the white dwarfs, scaled
    to the initial separation, and the vertical axis gives the elapsed
    time of the simulation, scaled to the time it would take two point masses
    to collide. The solid curve shows the analytical result,
    calculated from Newtonian mechanics, and the circles show the
    samples from the time evolution with \castro. For visual clarity, we 
    show only a small fraction of the timesteps.}
  \label{fig:freefall}
\end{figure}

@@

\begin{figure*}[ht]
  % Note that since we have periods in the filename, we need to double-
  % bracket the filename so that includegraphics doesn't think it's 
  % looking for something with the wrong extension. See:
  % http://tex.stackexchange.com/a/10575
  \centering
  \includegraphics[trim=0.75in 0.45in 0.85in 0.5in, clip, scale = 0.75]{{{plots/kh_t2.0_p2_low_res_collage}}}
  \caption{2D Kelvin-Helmholtz instability test at $t = 2.0$ for the initial 
    conditions given by \autoref{eq:kh_ic_b_ramp} and \autoref{eq:kh_ic_b}. 
    The rows each represent a different bulk fluid velocity $v$ and 
    the columns each represent a grid resolution $n$ (the number of 
    zones per spatial dimension). The highest velocity simulation, 
    $v=100$, corresponds to approximately Mach 70. Compare to 
    Robertson et al. (2010), Figure 7. \label{fig:kh_p2}}
\end{figure*}

@@

\begin{figure*}[ht]
  \centering
  \includegraphics[trim=0.75in 0.45in 0.85in 0.5in, clip, scale = 0.75]{{{plots/kh_t2.0_p3_low_res_collage}}}
  \caption{2D Kelvin-Helmholtz instability test at $t = 2.0$ for the initial 
    conditions given by \autoref{eq:kh_p3_rho} through \autoref{eq:kh_p3_vy}. 
    The meaning of the rows and columns is the same as in \autoref{fig:kh_p2}.
    \label{fig:kh_p3}  {\color{red} You should note this is $R_B$}}
\end{figure*}

@@

\begin{figure*}[ht]
  \includegraphics[trim = 0in 1.25in 0.25in 1.25in, clip, scale=0.65]{{{plots/kh_p3_high_res_collage}}}
  \caption{Time series of the Kelvin-Helmholtz problem proposed by McNally et al. (2012)
    as the simulation is just starting to go non-linear. The rows represent resolution, 
    where $n$ is the number of grid cells per spatial dimension, and the columns are 
    different snapshots in time.\label{fig:kh_p3_high_res}}
\end{figure*}

@@

\begin{figure}
  \centering
  \includegraphics[scale=0.45]{plots/single_star_compare_1e3_radius}
  \caption{A variation on \autoref{fig:single_star_static_radius} where
    we now compare the ``static'' case to ``motion'' simulations where the 
    star moves across the grid at a fixed linear speed. The lines represent 
    the effective number of zones per dimension inside the stellar material;
    due to the expanded size of the grid in the ``motion'' case, the 
    physical resolution is the same in each column in the legend.
    \label{fig:single_star_compare_radius}}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[scale=0.45]{plots/gravity_bcs}
  \caption{Absolute magnitude of the relative change in the distance of two unequal mass white dwarfs after one orbital period. 
           The stars were evolved in an inertial reference frame. The horizontal axis is the number of terms or multipole moments 
           captured in the series expansion for the potential at the domain boundary.\label{fig:gravity_bcs}}
\end{figure}

@@

\capstartfalse
\input{plots/sources.table}
\capstarttrue

@@

\begin{figure*}
  \centering
  \includegraphics[scale=0.7]{plots/circular_orbit_comparison}
  \caption{Positions of the white dwarfs in the orbital plane for four
    cases evolved over 25 orbital periods.  The $x$ and $y$ axes are
    normalized to the size of the domain, so that $x = -0.5$ is the
    left edge and $x = 0.5$ is the right edge. The dashed blue curve
    is the position of the primary white dwarf, and the solid red
    curve is the position of the secondary. In plot (a) we have the
    equal mass system evolved in the inertial reference frame, and in
    plot (c) we have the same system evolved in a rotating frame,
    where the positions have been transformed back to the inertial
    frame for comparison.  Plots (b) and (d) are analogous but for the
    unequal mass system.\label{fig:circular_orbit_comparison}}
\end{figure*}

@@

\begin{figure}
  \centering
  \includegraphics[scale=0.45]{plots/equal_energy_rot0}
  \caption{Absolute magnitude of the relative change in energy of two equal mass white dwarfs through 25 orbital periods,
           evolved in an inertial reference frame. The decline and recovery is a change in sign of the energy difference.
           \label{fig:energy_conservation_equal}}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[scale=0.45]{plots/unequal_angular_momentum_rot1}
  \caption{Absolute magnitude of the relative change in angular momentum of two unequal mass white dwarfs after 25 orbital periods, 
           evolved in a co-rotating reference frame. We consider only the component of the angular moment along the rotational 
           axis.
           \label{fig:angular_momentum_conservation_unequal}}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[scale=0.45]{plots/unequal_gw_rot0}
  \caption{Gravitational wave strain polarizations for the first two orbital periods of an 
           unequal mass system. The curves with markers are the numerical data, while the 
           curves without markers are the analytical results for two point masses.\label{fig:gw_strain}}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[scale=0.45]{plots/spatial_convergence_rot0}
  \caption{Distance between the two white dwarfs in the unequal mass system, for the first 
           10 seconds of their orbit. The distance is scaled by the initial orbital distance. 
           We plot at three different resolutions, corresponding to the number of 
           effective zones per dimension in the refined regions. Note that the $n = 1024$ curve
           falls nearly exactly on top of the $n = 512$ curve.\label{fig:unequal_spatial_convergence}}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[scale=0.4]{plots/weak_scaling}
  \caption{\castro\ weak scaling test, performed on Blue Waters at 
    NCSA. Each processor had a fixed amount of work, and we increased the 
    number of simulation zones in concert with the number of processors. The 
    solid curve represents perfect weak scaling, while the blue circles show 
    \castro's performance at each processor count. The vertical axis measures 
    the median time per timestep, normalized to this value for the smallest 
    processor count.\label{fig:weak_scaling}}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[scale=0.4]{plots/strong_scaling}
  \caption{\castro\ strong scaling test performed on the Blue Waters machine at
    NCSA. The vertical axis measures the median time per timestep, and the 
    horizontal axis measures the number of processors in the simulation. Data 
    points are normalized to the time per timestep for the smallest number 
    of processors. The green circles show the data for a simulation with one 
    AMR level (a single uniform grid), the blue diamonds show the data for a simulation with two AMR
    levels (one coarse and one fine), while the red circles show the data 
    for a test with three AMR levels (one coarse and two fine). The fine levels 
    increase the resolution only in the regions around the stars. For each case 
    we draw a solid curve representing perfect strong scaling.\label{fig:strong_scaling}}
\end{figure}

@@

\bibliographystyle{../apj}
\bibliography{../refs}

>>>>

\documentclass[iop,numberedappendix]{emulateapj}

@@

As a demonstration of the method's accuracy, we consider the case of two 
white dwarfs of mass ratio 2/3, using the initialization procedure described below 
in \autoref{sec:implementation}. We terminated the simulation just after
initialization, so that we perform only an initial Poisson solve for this 
density distribution. We did this for values of $l_{\text{max}}$ ranging
from 0 to 20, and we also did this using the numerically exact solution 
provided by \autoref{eq:direct_sum}.  Defining the $L^2$
norm of a field $f$ as
\begin{equation}
  \| f \|_2 = \left(\sum_{i,j,k} \Delta x\, \Delta y\, \Delta z\, f_{ijk}^2\right)^{1/2},
\end{equation}
we computed the $L^2$ error of $\Phi$ on the entire domain for multipole 
boundary conditions, which we call $\Phi_l$, relative to $\Phi$ 
obtained using the exact boundary conditions:
\begin{equation}
  \text{Error}_l = \frac{\|\Phi_l - \Phi_{\text{exact}}\|_2}{\|\Phi_{\text{exact}}\|_2}.
\end{equation}
The result is shown in \autoref{fig:bc_comparison}. At $l_{\text{max}} = 6$,
the error is already well below $10^{-4}$ and we adopt this as our default 
choice for all simulations with Poisson gravity. In \autoref{sec:kepler} we 
show that there are no gains to be had by increasing the accuracy further. At 
very high orders ($l \gtrsim 18$) the approximation breaks down, as seen in \autoref{fig:bc_comparison}. 
This is a result of the ambient material on the grid. At each boundary point we 
assume that all of the mass on the grid is contained within a sphere whose radius is 
the distance from that boundary point to the center of the domain. This does not hold 
for boundary points in the centers of domain faces, because of the material in the 
domain corners. This can be fixed by using multiple mass shells at diferent radii, but the error 
is negligible in practice for the values of $l_{\text{max}}$ that we use.
\begin{figure}[h]
  \centering
  \includegraphics[scale=0.45]{bc_comparison}
  \caption{Error of $\Phi$ on the computational domain for a binary white dwarf simulation 
    whose boundary conditions were computed using various values of the maximum multipole order,
    relative to the exact solution determined by a brute force sum on the boundaries.
    Circles represent the error at integer values, and they have been connected by a smooth 
    line to guide the eye.\label{fig:bc_comparison}}
\end{figure}

@@

We find that at low resolution convergence is actually substantially better 
than second-order. The explanation for this is that we are attempting to 
model a spherical object on a rectangular grid. This results in two sources of error.
First, at very low resolution, the object does not look very spherical due to the rectangular 
grid representation, so the potential it produces is not quite that of a sphere. 
As the resolution is increased, the distribution of the mass on the grid will change.
\begin{figure}[h]
  \centering
  \includegraphics[scale=0.45]{phi_comparison}
  \caption{Comparison of the \castro\ gravitational potential to the analytical solution for: 
    a sphere of uniform density; the same sphere, but with the potential normalized using the 
    actual amount of mass on the grid instead of the mass of a perfect sphere; and, a 
    cube of uniform density. Plotted also is a notional curve whose slope represents
    perfect second order convergence.\label{fig:gravity_convergence}}
\end{figure}
Second, the total amount of mass on the grid will change as the sphere fills out. 
So we are combining the true accuracy bonus from increased resolution 
with the artificial accuracy bonus from getting closer to solving the problem 
we are supposed to be solving. At high resolution this effect levels off, though, 
as the representation of the sphere is not significantly different in 
our two highest resolutions shown. For example, at $128$ zones per dimension 
the amount of mass on the grid happens to be slightly closer to the true spherical 
mass than at $256$ zones per dimension.
We can eliminate the second source of error by changing the density on  
the grid so that the total mass $M$ is actually what we intend it to be.
The resolution study for this case (the ``normalized sphere'') is also
plotted in \autoref{fig:gravity_convergence}. At low resolution we still obtain
convergence slightly better than second-order, indicating that we 
have not eliminated the geometrical problem of the mass distribution changing.

@@

Outside of the stars we fill the rest of the domain with a very low density 
ambient gas because our hydrodynamics model requires the density to be 
non-zero everywhere. This ambient material can create difficulties for the simulation.
In addition to the negative densities or energies at the stellar surfaces mentioned earlier, 
in the rotating reference frame we observe that standing instabilities can create very 
large velocities in the ambient fluid that drag down the global timestep by 
up to an order of magnitude.  To deal with this we employ a ``sponge'' similar 
to that described by \citet{maestro3} for the outer regions of the computational domain. 
After the hydrodynamics update, we apply a damping force to the momentum
equation as follows:
\begin{equation}
  (\rho \mathbf{u})^{n+1} \to \frac{(\rho \mathbf{u})^{n+1}}{1 + (\Delta t / \Delta t_S) f_S},
\end{equation} 
where $\Delta t_S$ is a timescale for the sponge to operate on, and
$f_S$ is the damping factor.  We choose it so that that the sponge is
non-operational inside a radius $r_S$ from the origin, and fully
applied at a radius $r_S^\prime \equiv r_S + \Delta r_S$. We then
smooth the sponge out between $r_S$ and $r_S^\prime$:
\begin{equation}
  f_{S} = \begin{dcases} 0 & r < r_S \\ \frac{1}{2}\left(1 - \text{cos}\left[\pi\left(\dfrac{r - r_S}{\Delta r_S}\right)\right]\right) & r_S \leq r < r_S^\prime \\ 1 & r \geq r_S^\prime. \end{dcases}\label{eq:sponge_frac}
\end{equation}
For the simulations in this paper we set $r_S$ to be 75\% of the 
distance from the origin to the domain boundaries, and $\Delta r_S$ so
that the sponge smoothing region extends another 10\% of that distance.
The resulting profile is displayed in \autoref{fig:sponge}. We set $\Delta
t_S = 0.01$ s, which is of the same order as the CFL timestep
for typical problem setups. While the sponge is applied we should avoid imputing any physical 
meaning to what is happening in the low-density gas far from the stars.
\begin{figure}
  \centering
  \includegraphics[scale=0.4]{sponge}
  \caption{Radial profile of the hydrodynamical sponge we apply (\autoref{eq:sponge_frac}). 
           We subtract $f_S$ from unity; the value of $1 - f_S$ indicates what happens 
           to the sponged function after the sponge is applied. The sponge has no effect 
           in the inner part of the domain, and is fully applied at the outer edge.\label{fig:sponge}}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[scale=0.45]{single_star_static_1e3_radius}
  \caption{Time evolution of the effective radius of a $0.9 \msolar$ 
    white dwarf, seeded onto the grid using a one-dimensional hydrostatic
    model and evolved without further relaxation. The lines represent 
    different number of zones per spatial dimension; when this number is 
    greater than 256, it represents an effective resolution obtained 
    using AMR levels that cover the star. The radius is determined 
    using the volume of the grid that has a density greater than $10^3\ \text{g cm}^{-3}.$
    \label{fig:single_star_static_radius}}
\end{figure}

@@

We loaded a single star of mass $0.9\ \msolar$ onto the grid at the
origin, and evolved it for 200 seconds. Our diagnostic of choice is
the effective radius of the star, determined by the volume of the grid
that has a density greater than $10^3\ \text{g cm}^{-3}$ (see
\autoref{sec:implementation} for details on this measure). This choice
of density is intended to mark a reasonable outer edge to the star
that is not immediately susceptible to the numerical errors prevalent
near the physical edge of the star.
\autoref{fig:single_star_static_radius} shows our results at various
resolutions.  As expected, the star quickly approaches an equilibrium
size that is different (and in this case larger) than the
one-dimensional model, though the magnitude of this change becomes
smaller with resolution. The star is only approximately in equilibrium 
by this measure when the coarse grid of $256^3$ zones has a level of 
refinement that jumps by a factor of four. Even then there is a slight uptick
in the size toward the end, implying that the numerical stability is
not guaranteed for arbitrarily long timescales. For another view, we 
consider the kinetic energy on the grid, in \autoref{fig:single_star_static_ke}. 
This is a more holistic measure that weights the contribution by the density. 
At the end of the simulation the kinetic energy is not lower at the highest 
resolution than at the lower resolutions. This result suggests
that when constructing the equilibrium initial models that will form the
basis of later calculations, we should carefully monitor the evolution
of the stars when applying any artificial damping to cause the
merger, to ensure that the merger is due to this applied force and not
the intrinsic numerical instability of the stars.
\begin{figure}
  \centering
  \includegraphics[scale=0.45]{single_star_static_ke}
  \caption{Time evolution of the kinetic energy of a $0.9\, \msolar$ 
    white dwarf. The lines have the same meaning as in \autoref{fig:single_star_static_radius}.
    \label{fig:single_star_static_ke}}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[scale=0.45]{freefall}
  \caption{Time evolution of two initially stationary white dwarfs,
    mutually attracted to each other by the gravitational force. The
    horizontal axis gives the separation of the white dwarfs, scaled
    to the initial separation, and the vertical axis gives the elapsed
    time of the simulation, scaled to the time it would take two point masses
    to collide. The solid curve shows the analytical result,
    calculated from Newtonian mechanics, and the circles show the
    samples from the time evolution with \castro. For visual clarity, we 
    show only a small fraction of the timesteps.}
  \label{fig:freefall}
\end{figure}

@@

\begin{figure*}[ht]
  % Note that since we have periods in the filename, we need to double-
  % bracket the filename so that includegraphics doesn't think it's 
  % looking for something with the wrong extension. See:
  % http://tex.stackexchange.com/a/10575
  \centering
  \includegraphics[trim=0.75in 0.45in 0.85in 0.5in, clip, scale = 0.75]{{{kh_t2.0_p2_low_res_collage}}}
  \caption{2D Kelvin-Helmholtz instability test at $t = 2.0$ for the initial 
    conditions given by \autoref{eq:kh_ic_b_ramp} and \autoref{eq:kh_ic_b}. 
    The rows each represent a different bulk fluid velocity $v$ and 
    the columns each represent a grid resolution $n$ (the number of 
    zones per spatial dimension). The highest velocity simulation, 
    $v=100$, corresponds to approximately Mach 70. Compare to 
    Robertson et al. (2010), Figure 7. \label{fig:kh_p2}}
\end{figure*}

@@

\begin{figure*}[ht]
  \centering
  \includegraphics[trim=0.75in 0.45in 0.85in 0.5in, clip, scale = 0.75]{{{kh_t2.0_p3_low_res_collage}}}
  \caption{2D Kelvin-Helmholtz instability test at $t = 2.0$ for the initial 
    conditions given by \autoref{eq:kh_p3_rho} through \autoref{eq:kh_p3_vy}. 
    The meaning of the rows and columns is the same as in \autoref{fig:kh_p2}.
    \label{fig:kh_p3}  {\color{red} You should note this is $R_B$}}
\end{figure*}

@@

\begin{figure*}[ht]
  \includegraphics[trim = 0in 1.25in 0.25in 1.25in, clip, scale=0.65]{{{kh_p3_high_res_collage}}}
  \caption{Time series of the Kelvin-Helmholtz problem proposed by McNally et al. (2012)
    as the simulation is just starting to go non-linear. The rows represent resolution, 
    where $n$ is the number of grid cells per spatial dimension, and the columns are 
    different snapshots in time.\label{fig:kh_p3_high_res}}
\end{figure*}

@@

\begin{figure}
  \centering
  \includegraphics[scale=0.45]{single_star_compare_1e3_radius}
  \caption{A variation on \autoref{fig:single_star_static_radius} where
    we now compare the ``static'' case to ``motion'' simulations where the 
    star moves across the grid at a fixed linear speed. The lines represent 
    the effective number of zones per dimension inside the stellar material;
    due to the expanded size of the grid in the ``motion'' case, the 
    physical resolution is the same in each column in the legend.
    \label{fig:single_star_compare_radius}}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[scale=0.45]{gravity_bcs}
  \caption{Absolute magnitude of the relative change in the distance of two unequal mass white dwarfs after one orbital period. 
           The stars were evolved in an inertial reference frame. The horizontal axis is the number of terms or multipole moments 
           captured in the series expansion for the potential at the domain boundary.\label{fig:gravity_bcs}}
\end{figure}

@@

\capstartfalse
\input{sources.table}
\capstarttrue

@@

\begin{figure*}
  \centering
  \includegraphics[scale=0.7]{circular_orbit_comparison}
  \caption{Positions of the white dwarfs in the orbital plane for four
    cases evolved over 25 orbital periods.  The $x$ and $y$ axes are
    normalized to the size of the domain, so that $x = -0.5$ is the
    left edge and $x = 0.5$ is the right edge. The dashed blue curve
    is the position of the primary white dwarf, and the solid red
    curve is the position of the secondary. In plot (a) we have the
    equal mass system evolved in the inertial reference frame, and in
    plot (c) we have the same system evolved in a rotating frame,
    where the positions have been transformed back to the inertial
    frame for comparison.  Plots (b) and (d) are analogous but for the
    unequal mass system.\label{fig:circular_orbit_comparison}}
\end{figure*}

@@

\begin{figure}
  \centering
  \includegraphics[scale=0.45]{equal_energy_rot0}
  \caption{Absolute magnitude of the relative change in energy of two equal mass white dwarfs through 25 orbital periods,
           evolved in an inertial reference frame. The decline and recovery is a change in sign of the energy difference.
           \label{fig:energy_conservation_equal}}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[scale=0.45]{unequal_angular_momentum_rot1}
  \caption{Absolute magnitude of the relative change in angular momentum of two unequal mass white dwarfs after 25 orbital periods, 
           evolved in a co-rotating reference frame. We consider only the component of the angular moment along the rotational 
           axis.
           \label{fig:angular_momentum_conservation_unequal}}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[scale=0.45]{unequal_gw_rot0}
  \caption{Gravitational wave strain polarizations for the first two orbital periods of an 
           unequal mass system. The curves with markers are the numerical data, while the 
           curves without markers are the analytical results for two point masses.\label{fig:gw_strain}}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[scale=0.45]{spatial_convergence_rot0}
  \caption{Distance between the two white dwarfs in the unequal mass system, for the first 
           10 seconds of their orbit. The distance is scaled by the initial orbital distance. 
           We plot at three different resolutions, corresponding to the number of 
           effective zones per dimension in the refined regions. Note that the $n = 1024$ curve
           falls nearly exactly on top of the $n = 512$ curve.\label{fig:unequal_spatial_convergence}}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[scale=0.4]{weak_scaling}
  \caption{\castro\ weak scaling test, performed on Blue Waters at 
    NCSA. Each processor had a fixed amount of work, and we increased the 
    number of simulation zones in concert with the number of processors. The 
    solid curve represents perfect weak scaling, while the blue circles show 
    \castro's performance at each processor count. The vertical axis measures 
    the median time per timestep, normalized to this value for the smallest 
    processor count.\label{fig:weak_scaling}}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[scale=0.4]{strong_scaling}
  \caption{\castro\ strong scaling test performed on the Blue Waters machine at
    NCSA. The vertical axis measures the median time per timestep, and the 
    horizontal axis measures the number of processors in the simulation. Data 
    points are normalized to the time per timestep for the smallest number 
    of processors. The green circles show the data for a simulation with one 
    AMR level (a single uniform grid), the blue diamonds show the data for a simulation with two AMR
    levels (one coarse and one fine), while the red circles show the data 
    for a test with three AMR levels (one coarse and two fine). The fine levels 
    increase the resolution only in the regions around the stars. For each case 
    we draw a solid curve representing perfect strong scaling.\label{fig:strong_scaling}}
\end{figure}

@@

\bibliographystyle{apj}
\input{paper.bbl}
